Pairwise-complete correlation considered dangerous

### 2015-05-30 missing.Rmd
typo

The `use="complete"` option is one way to deal with missing values. It simply removes rows of the matrix `x` with missing observations. Since the third through fifth rows of our example matrix
are all identical we expect perfect correlation across the board, and indeed:
```{r}
cor(x, use="complete")
```
Reasonable people might question this approach. Deleting two observations has a huge effect on the correlation between `x[,1]` and `x[,2]` in this example mostly because of the large change in `x[,1]`. The result really says that we should collect more observations!

>>>>

The `use="complete"` option is one way to deal with missing values. It simply removes rows of the matrix `x` with missing observations. Since the columns of the  third through fifth rows of our example matrix
are all identical we expect perfect correlation across the board, and indeed:
```{r}
cor(x, use="complete")
```
Reasonable people might question this approach. Deleting two observations has a huge effect on the correlation between `x[,1]` and `x[,2]` in this example mostly because of the large change in `x[,1]`. The result really says that we should collect more observations!
